WordRec Experiment

### 2019-04-10 Data_and_analysis/analyses.Rmd
more revisions

feather::write_feather(parameters, "saved_data/parameters.feather")
parameters <- feather::read_feather("saved_data/parameters.feather")

@@

feather::write_feather(pred_uni, "saved_data/pred_uni.feather")
pred_uni <- feather::read_feather("saved_data/pred_uni.feather")

@@

feather::write_feather(pred_bimod, "saved_data/all_bimod.feather")
pred_bimod <- feather::read_feather("saved_data/all_bimod.feather")
```
main plot 
```{r}
pred_bimod$model <- factor(pred_bimod$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))

@@

@@

#Sound Unimodal
fit_s <- function(data) {
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), 
                 data=data,
                 start = list(e=0, vrA=1),
                 nls.control(warnOnly = TRUE)) 
}
#Concept Unimodal
fit_c <- function(data) {
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), 
                 data=data,
                 start = list(e=0, vrV=1),
                 nls.control(warnOnly = TRUE)) 
}

#Joint sound-concept
fit_j <- function(data) {
  nls(answer ~1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), 
                 data=data,
                 start = list(e=0, vrA_j=1, vrV_j=1),
                 nls.control(warnOnly = TRUE)) 
}

@@

exp4_good_s <- exp4_good %>% filter(condition =='sound')
exp4_good_c <- exp4_good %>% filter(condition =='concept')
exp4_good_j <- exp4_good %>% filter(condition =='joint')

#Split data by subject 
data_by_subj_s <- split(exp4_good_s, exp4_good_s$ID) 
data_by_subj_c <- split(exp4_good_c, exp4_good_c$ID)
data_by_subj_j <- split(exp4_good_j, exp4_good_j$ID)

#.. and fit
model_by_subj_s <- map(data_by_subj_s, fit_s) 
model_by_subj_c <- map(data_by_subj_c, fit_c)
model_by_subj_j <- map(data_by_subj_j, fit_j)

@@

#Unimodal coefficients
 co_uni <- function(model, ID) {
   data.frame(bias=coefficients(model)[1], 
              variance=coefficients(model)[2], 
              ID=ID)
 }

 #Bimodal coefficients
 co_bim <- function(model, ID) {
   data.frame(bias=coefficients(model)[1],
              var_s=coefficients(model)[2],
              var_c=coefficients(model)[3],
              ID=ID)
 }

@@

#Here extract ceofficients to build optimal model later
coef_s <- map2(model_by_subj_s, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrA_u= variance,
         bA_u =  bias)

coef_c <- map2(model_by_subj_c, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrV_u= variance,
         bV_u =  bias)

coef_j <- map2(model_by_subj_j, ID, co_bim) %>%
  bind_rows() %>%
  rename(vrA_j = var_s,
         vrV_j = var_c,  
         b =  bias)

@@

data_models <- exp_good %>%
  filter(condition == "joint",
         experiment == "Experiment4") %>%
  group_by(ID, concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  left_join(coef_s) %>%
  left_join(coef_c) %>%
  left_join(coef_j)

@@

data_by_subj <- split(data_models, data_models$ID)

@@

```{r}
weight <- data_models %>%
  group_by(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  select(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  unique() %>%
  mutate(weight_u = vrA_u/vrV_u,
         weight_b = vrA_j/vrV_j) %>%
  mutate(prop = weight_u/weight_b)

feather::write_feather(weight, "ind_weights.feather")
weight <- feather::read_feather("ind_weights.feather")

weight_separate <- weight %>%
  select(ID, weight_u, weight_b) %>%
  gather (key, value, weight_u, weight_b)

weight.boot <- boot(data=weight$prop, function(x,i) median(x[i]), R=10000)

weight.ci=boot.ci(weight.boot, 
                  conf = 0.95,
                  type = c('perc'))

#weights.dist <- weight$prop[weight$prop < 100 & weight$prop > 0.01]

weight.median <- weight.ci$t0
weight.median_low <- weight.ci$percent[4]
weight.median_up <- weight.ci$percent[5]

ggplot(data=weight, aes(x=prop, y=..count..)) +
  geom_histogram(alpha=0.5, binwidth = 0.4)+
  geom_vline(xintercept = weight.median, col='red')+
  geom_vline(xintercept = weight.median_low, linetype='dashed') +
  geom_vline(xintercept = weight.median_up, linetype='dashed') +
  #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
  #geom_histogram(binwidth = 0.2) +
 scale_x_log10(breaks =c(0.1,1,10)) +
   xlab("Optimal weighing relative to real weighing") +ylab("Count")+
  theme_few()+
  theme(aspect.ratio = 0.7) +
  coord_cartesian(xlim=c(0.01,100))

@@

>>>>

#feather::write_feather(parameters, "saved_data/parameters.feather")
parameters <- feather::read_feather("saved_data/parameters.feather")

@@

#feather::write_feather(pred_uni, "saved_data/pred_uni.feather")
pred_uni <- feather::read_feather("saved_data/pred_uni.feather")

@@

#feather::write_feather(pred_bimod, "saved_data/all_bimod.feather")
pred_bimod <- feather::read_feather("saved_data/all_bimod.feather")
```

main plot 
```{r}
pred_bimod$model <- factor(pred_bimod$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))

@@

First simulate answers based on the population level probabilistic model (we will analyse both real and simualted answers simultaneousely)
```{r}
#First define all models,

param <- parameters %>%
  filter(experiment =="Experiment4")

vrA = param$var_s
  bA = param$bias_s

vrV = param$var_c
  bV = param$bias_c

vrAj = param$var_j_s
vrVj = param$var_j_c
  bj = param$bias_j

# Sound only
model_s <- function (x,y) {
  1/(1 + (1-bA)*exp((-4/vrA)*x+(8/vrA)))
}

# Visual only
model_c <- function (x,y) {
  1/(1 + (1-bV)*exp((-4/vrV)*y+(8/vrV)))
}

# Optimal
model_opt <- function (x,y) {

  1/(1 + (1-bj)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
}

# Descriptive
model_des <- function (x,y) {
  1/(1 + (1-bj)*exp((-4/vrAj)*x+(-4/vrVj)*y+(8/vrAj)+(8/vrVj)))
}

exp4_s <- exp4_good %>% filter(condition =='sound')
exp4_c <- exp4_good %>% filter(condition =='concept')
exp4_j <- exp4_good %>% filter(condition =='joint')

#Simulate sounds
exp4_both_s <- exp4_s %>%
  mutate(prob = model_s(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer_simu = rbinom(1, 1, prob=prob))

exp4_both_c <- exp4_c %>%
  mutate(prob = model_c(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer_simu = rbinom(1, 1, prob=prob))

exp4_both_j <- exp4_j %>%
  mutate(prob = model_des(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer_simu = rbinom(1, 1, prob=prob))

#next used this new dataset to run the rest of the code

@@

#Sound Unimodal
fit_s <- function(data) {
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), 
                 data=data,
                 start = list(e=0, vrA=1),
                 nls.control(warnOnly = TRUE)) 
}

fit_simu_s <- function(data) {
  nls(answer_simu ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), 
                 data=data,
                 start = list(e=0, vrA=1),
                 nls.control(warnOnly = TRUE)) 
}
#Concept Unimodal
fit_c <- function(data, response) {
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), 
                 data=data,
                 start = list(e=0, vrV=1),
                 nls.control(warnOnly = TRUE)) 
}

fit_simu_c <- function(data, response) {
  nls(answer_simu ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), 
                 data=data,
                 start = list(e=0, vrV=1),
                 nls.control(warnOnly = TRUE)) 
}

#Joint sound-concept
fit_j <- function(data, response) {
  nls(answer ~1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), 
                 data=data,
                 start = list(e=0, vrA_j=1, vrV_j=1),
                 nls.control(warnOnly = TRUE)) 
}

fit_simu_j <- function(data, response) {
  nls(answer_simu ~1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), 
                 data=data,
                 start = list(e=0, vrA_j=1, vrV_j=1),
                 nls.control(warnOnly = TRUE)) 
}

@@

#Split data by subject 
data_by_subj_s <- split(exp4_both_s, exp4_both_s$ID) 
data_by_subj_c <- split(exp4_both_c, exp4_both_c$ID)
data_by_subj_j <- split(exp4_both_j, exp4_both_j$ID)

# fit the empirical data
model_by_subj_s <- map(data_by_subj_s, fit_s) 
model_by_subj_c <- map(data_by_subj_c, fit_c)
model_by_subj_j <- map(data_by_subj_j, fit_j)

#.. and the simulated data
model_by_subj_simu_s <- map(data_by_subj_s, fit_simu_s) 
model_by_subj_simu_c <- map(data_by_subj_c, fit_simu_c)
model_by_subj_simu_j <- map(data_by_subj_j, fit_simu_j)

## Convergence info

@@

#Unimodal coefficients
 co_uni <- function(model, ID) {
   data.frame(bias=coefficients(model)[1], 
              variance=coefficients(model)[2], 
              convergence=model$convInfo$stopMessage,
              ID=ID)
 }

 #Bimodal coefficients
 co_bim <- function(model, ID) {
   data.frame(bias=coefficients(model)[1],
              var_s=coefficients(model)[2],
              var_c=coefficients(model)[3],
              convergence=model$convInfo$stopMessage,
              ID=ID)
 }

@@

#Here extract ceofficients to build optimal model later
coef_s <- map2(model_by_subj_s, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrA_u= variance,
         bA_u =  bias,
         conv_A = convergence)

coef_simu_s <- map2(model_by_subj_simu_s, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrA_u= variance,
         bA_u =  bias,
         conv_A = convergence)

coef_c <- map2(model_by_subj_c, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrV_u= variance,
         bV_u =  bias,
         conv_V = convergence)

coef_simu_c <- map2(model_by_subj_simu_c, ID, co_uni) %>%
  bind_rows() %>%
  rename(vrV_u= variance,
         bV_u =  bias,
         conv_V = convergence)

coef_j <- map2(model_by_subj_j, ID, co_bim) %>%
  bind_rows() %>%
  rename(vrA_j = var_s,
         vrV_j = var_c,  
         b =  bias,
         conv_j = convergence)

coef_simu_j <- map2(model_by_subj_simu_j, ID, co_bim) %>%
  bind_rows() %>%
  rename(vrA_j = var_s,
         vrV_j = var_c,  
         b =  bias,
         conv_j = convergence)

@@

data_models <- exp_good %>%
  filter(condition == "joint",
         experiment == "Experiment4") %>%
  group_by(ID, concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  ungroup() %>%
  left_join(coef_s) %>%
  left_join(coef_c) %>%
  left_join(coef_j)

data_models_simu <- exp_good %>%
  filter(condition == "joint",
         experiment == "Experiment4") %>%
  group_by(ID, concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  ungroup() %>%
  left_join(coef_simu_s) %>%
  left_join(coef_simu_c) %>%
  left_join(coef_simu_j)

data_models_good <- data_models %>%
  filter(conv_A == "converged",
         conv_V == "converged",
         conv_j == "converged")

data_models_good_simu <- data_models_simu %>%
  filter(conv_A == "converged",
         conv_V == "converged",
         conv_j == "converged")

N_conv <- data_models_good %>% 
  distinct(ID) %>%
  nrow()

N_conv_simu <- data_models_good_simu %>% 
  distinct(ID) %>%
  nrow()

@@

data_by_subj <- split(data_models_good, data_models_good$ID)

@@

```{r}
weight <- data_models_good %>%
  group_by(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  select(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  unique() %>%
  mutate(weight_u = vrA_u/vrV_u,
         weight_b = vrA_j/vrV_j) %>%
  mutate(prop = weight_u/weight_b) %>%
  mutate(type='real')

weight_simu <- data_models_good_simu %>%
  group_by(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  select(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  unique() %>%
  mutate(weight_u = vrA_u/vrV_u,
         weight_b = vrA_j/vrV_j) %>%
  mutate(prop = weight_u/weight_b) %>%
  mutate(type='simulated')

weight_both <- weight %>%
  bind_rows(weight_simu)

#feather::write_feather(weight, "ind_weights.feather")
#weight <- feather::read_feather("ind_weights.feather")

weight_simu_low <- quantile(weight_simu$prop, 0.05)
weight_simu_high <- quantile(weight_simu$prop, 0.95)

ggplot(data=weight_both, aes(x=prop, y=..ncount..)) +
  #geom_histogram(data=subset(weight_both, data=='real'), fill="red", alpha=0.2, binwidth = 0.4)+
  geom_histogram(data=subset(weight_both, data=='simulated'), fill="blue", alpha=0.1, binwidth = 0.4)+
  #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
  #geom_histogram(binwidth = 0.2) +
  geom_vline(xintercept = weight_simu_low, linetype='dashed') +
  geom_vline(xintercept = weight_simu_high, linetype='dashed')+
 scale_x_log10(breaks =c(0.1,1,10)) +
   xlab("Optimal weighing relative to real weighing") +ylab("Count")+
  theme_few()+
  theme(aspect.ratio = 0.7) #+
  #coord_cartesian(xlim=c(0.01,100))

@@

Simulat random responses from the population level model

First, take the real experimental data
```{r}
exp_exp4_s <- exp_good %>%
  filter(condition =="sound",
         experiment == "Experiment4")

exp_exp4_c <- exp_good %>%
  filter(condition =="concept",
         experiment == "Experiment4")

exp_exp4_j <- exp_good %>%
  filter(condition =="joint",
         experiment == "Experiment4")
```

Then, instead of the real answers, simulate new answers from the population-level model

#What does the mean data say 
#generate two data point from a binomial with probabilty model_fit1()
#loop over visual and auditory distance/ or create  adataframe with

#For each subject, simulate the auditory, and visual responses as well as bimodal (descriptive) mod

simulations <- data.frame()
#x <- c("ID", "bimod")
#colnames(simlations) <- x

#

for (i in 1:50) {
Simul_exp1 <- joint_all_exp1 %>%
  select(ID, sound_dist, concept_dist) %>%
  mutate(prob = model_fit1(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer = rbinom(1, 1, prob=prob))

joint_bysub_sim_1 <- Simul_exp1 %>%
  group_by(ID) %>%
  do(fit_joint_sim_1 = glm(answer ~ concept_dist+ sound_dist, data=., family = binomial()))

bimodal_bysub_sim_1 = tidy(joint_bysub_sim_1, fit_joint_sim_1) %>%
  filter(term == 'concept_dist' | term == 'sound_dist') %>%
  mutate(j_var = 4/(estimate)) %>%
  select(ID, term, j_var) %>%
  spread(term, j_var) %>%
  rename(j_c_var = concept_dist, 
         j_s_var = sound_dist) %>%
  mutate(bimod = j_c_var/j_s_var) %>%
  select(ID, bimod) %>%
  filter(bimod > 0.1) %>%
  filter(bimod < 10)

  simulations <- bind_rows(simulations, bimodal_bysub_sim_1)
}

  #I need to take the average of this over multiple runs

  bimod_sim <- simulations  %>%
    mutate(data='simulation')

  bimod_real <- bimodal_bysub_good_1  %>%
    select(ID, bimod) %>%
    mutate(data='real')

  #n_remove <- nrow(bimod_sim)-nrow(bimod_real)

  #bimod_sim <- head(bimod_sim, -n_remove)

  bimod_all <- bind_rows(bimod_real, bimod_sim)
